---
title: "HW10"
author: "Zirui Zhang"
date: "2023-05-02"
output: html_document
---
```{r message=FALSE}
library(dplyr)
library(survival)
library(MASS)
library(KMsurv)
library(survminer)
```

### Question 1

```{r}
# build data frame
time = c(4, 12, 15, 21, 23,
         2, 6, 8, 10, 19)
cens = c(0, 1, 0, 1, 0,
         0, 1, 1, 0, 0)
group = c(rep("group1", 5),
          rep("group2", 5))
df = data.frame(time, cens, group)
# log-rank test
survdiff(Surv(time, cens)~group, data = df)
```
The p-value of the chi-sq test is 0.3>0.05, thus we fail to reject the null and conclude that there's no significant difference between the hazard function of the two groups.

### Question 2

```{r}
data(kidtran)
kidtran %>% head(10)
# for male group
KM1 = survfit(Surv(time, delta)~race, data = subset(kidtran, gender == 1), conf.type = "log")
plot(KM1, conf.int = F, mark.time = T, 
     xlab = "Time", ylab = "Survival Probability", main = "Male K-M curve",
     col = c("pink", "dark green"),
     cex.lab = 1.5, cex.main = 1.5)
legend('topright', c("white", "black"), lty=1, col = c("pink", "dark green"))
# for female group
KM2 = survfit(Surv(time, delta)~race, data = subset(kidtran, gender == 2), conf.type = "log")
plot(KM2, conf.int = F, mark.time = T, 
     xlab = "Time", ylab = "Survival Probability", main = "Female K-M curve",
     col = c("pink", "dark green"),
     cex.lab = 1.5, cex.main = 1.5)
legend('topright', c("white", "black"), lty=1, col = c("pink", "dark green"))
```

### Question 3

```{r}
data(larynx)
larynx %>% head(10)
attach(larynx)
Z1 = as.numeric(stage == 2)
Z2 = as.numeric(stage == 3)
Z3 = as.numeric(stage == 4)
Z4 = age
fit2 = coxph(Surv(time, delta)~Z1+Z2+Z3+Z4+Z1*Z4, data=larynx, method = 'breslow')
summary(fit2)
```
- Explanation:

Z1, Z3 and Z1*Z4 are significant variables. Holding the age, the HR between patients in stage II and patients in stage I is `r round(exp(fit2$coefficients[1]), 2)`, HR between patients in stage III and patients in stage I is `r round(exp(fit2$coefficients[2]), 2)`,HR between patients in stage IV and patients in stage I is `r round(exp(fit2$coefficients[3]), 2)`. When a patient is in stage I, one unit increase in age would increase the probability of death by `r scales::percent(round(exp(fit2$coefficients[4]), 4)-1)`.When a patient is in stage II, one unit increase in age would increse the probability of death by `r scales::percent(round(exp(fit2$coefficients[5]), 2)-1)`.


- HR:

For a stage II patient of age 50, Z1=1, Z4=50; for a stage I patient of age 50, Z1=0, Z4=50. The probability of death at given time t of the former is `r round(exp(fit2$coefficients[1]*1 + fit2$coefficients[5]*1*50 - 0), 2)` times the probability of death of the latter. 



